---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Hannah Barham"
output: 
 html_document:
   theme: cerulean
   highlight: espresso 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse) 

```

<br><br>

## Introduction

This dataset includes metadata from Spotify's API with 6 genres and thousands of songs. It ranks these songs and categories according to artist, genre, and other variables while also ranking cool things like danceability, tempo, key, and much more. I think this dataset would be interesting to work with being as a spend a lot of my free time listening to music on Spotify, including a lot of the artists mentioned so it would be fun to see what kind of information I can find from this data. [Spotify Songs](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-21/readme.md).

```{r read-examine-data}
spotify_songs <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv")
dplyr::glimpse(spotify_songs)
```

<br><br>

## Question 1

#### Which playlist genre had the highest average dancebility?

### Methods 
``` {r Highest_Mean_Danceability}
spotify_songs %>% 
  group_by(playlist_genre) %>%
  summarize(dance_bar_height=mean(danceability),        
            dance_label_height = dance_bar_height+0.035, 
            dance_label_rounded = round(dance_bar_height,3) ) %>%
  ungroup() %>%
  ggplot(aes(x=playlist_genre)) +
  geom_col(aes(y= dance_bar_height),fill= "pink", color= "black")+
  geom_text(aes(y= dance_label_height,
                label=dance_label_rounded))+
  labs(x= "Playlist Genre", y= "Danceability")
``` 
   
### Answer 

Rap had the highest average danceability.


<br><br>

## Question 2

#### Which featured The Tempations song had the lowest track popularity?

### Methods

```{r Temptations_Popularity, fig.height=5, fig.width=8.5}
spotify_songs %>%
  filter(track_artist== "The Temptations") %>%
  select(track_popularity, track_name) %>%
  ggplot(aes(y=track_popularity, x=track_name)) +
  geom_col(fill= "lavender", color= "pink")+
  labs(x="The Temptations Track Names", y="Track Popularity")+
  theme_dark()
  

```

### Answer

"Papa Was A Rollin' Stone" had the lowest track popularity. 

<br><br>

## Question 3

#### Between genres dance pop, pop remix, and dance room which had the longest duration? 

### Methods
```{r Playlist_Duration}
my_playlists <- c("Dance Room", "Pop Remix", "Dance Pop")
spotify_songs %>%
  filter(playlist_name %in% my_playlists) %>%
  select(playlist_name, duration_ms) %>%
  group_by(playlist_name) %>%
  summarize(ms_bar_height=sum((duration_ms)/1000)/60) %>%
  ungroup() %>%
  ggplot(aes(x=playlist_name)) +
  geom_col(aes(y= ms_bar_height),fill= "light green", color= "black")+
  labs(x= "Playlist Name", y= "Duration (minutes)")+
  theme_classic()
  
  
```

### Answer

Dance Room had the shortest duration.


<br><br>

## Question 4

#### Are India.Arie's song energy and tempo positively or negatively correlated?

### Methods
``` {r India.Arie, fig.length=5, fig.width=6}
spotify_songs %>%
  filter(track_artist== "India.Arie") %>%
  select(energy, tempo) %>%
  ggplot()+
  aes(y=energy, x=tempo)+
  geom_point(size=2.5, color="purple")+
  geom_smooth(method="lm", color="black")+
  labs(x="Tempo (BPM)", y="Energy", title="India.Arie's Song Energy and Tempo")+
  theme_classic()
```

### Answer

India.Arie's song energy and tempo are positively correlated. 
