---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Hannah Barham"
output: 
 html_document:
   theme: cerulean
   highlight: espresso 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse) 

```

<br><br>

## Introduction

This dataset includes metadata from Spotify's API with 6 genres and thousands of songs. It ranks these songs and categories according to artist, genre, and other variables while also ranking cool things like danceability, tempo, key, and much more. I think this dataset would be interesting to work with being as a spend a lot of my free time listening to music on Spotify, including a lot of the artists mentioned so it would be fun to see what kind of information I can find from this data. [Spotify Songs](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-21/readme.md).

```{r read-examine-data}
spotify_songs <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv")
dplyr::glimpse(spotify_songs)
```

<br><br>

## Question 1

#### Which playlist genre had the highest average dancebility?

### Methods 
``` {r Highest_Mean_Danceability}
spotify_songs %>% 
  group_by(playlist_genre) %>%
  summarize(dance_bar_height=mean(danceability),        
            dance_label_height = dance_bar_height+0.035, 
            dance_label_rounded = round(dance_bar_height,3) ) %>%
  ungroup() %>%
  ggplot(aes(x=playlist_genre)) +
  geom_col(aes(y= dance_bar_height),fill= "pink", color= "black")+
  geom_text(aes(y= dance_label_height,
                label=dance_label_rounded))+
  labs(x= "Playlist Genre", y= "Danceability")
``` 
   
### Rap had the highest average dancebility. 

Replace this text with your answer to your question.


<br><br>

## Question 2

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

### Answer

Replace this text with your answer to your question.
